|

### 2020-09-17 paper.Rmd
second pass at discussion

The sage display is easily incorporated into exploratory high dimensional data analysis
tasks: classification, clustering, and search. For classification tasks,
as shown in the sketches example, the sage display decreases the number of 
overlapping points between classes and provides better visual separation between
classes compared to the regular tour.  For clustering tasks, as shown in the 
single cell RNA-seq example, the sage display uncovered clusters that were 
originally obscured by data piling. Furthermore, unlike some
non-linear dimension reduction (NLDR) techniques like t-SNE, the sage display 
still gives the viewer an accurate assessment of the size of a cluster, 
and their relative orientation. We learned that the highlighted 
The single cell RNA-seq case study uncovered clusters that were originally obscured by data piling;

as we saw in our single cell example. Our parameter tuning example highlights that the sage display is linear up to a given effective dimension. As a result, the sage display provides interpretable visualisations while preserving global structure in the high dimensional space, as highlighted in the particle physics example.

@@

For the sage display tuning is often required to avoid bunching points in the visualisation, especially if the projection is dense in the center of the distribution. However, given that the display is quick to compute, it is easy to try out different parameter combinations. Expanding around the center too aggressively can also introduce distortions in the display, which is also a problem for NLDR methods.

Currently, the sage display is naive to information in high dimensional space that is not captured by linear projections. Further work is required to investigate other transformations of the projections that can capture non-linear structure or that are locally linear, like the transformations performed by t-SNE.

Add note on interactivity to tuning paragraph. Add a paragraph on applications, correlation

>>>>

@@

The sage display is easily incorporated into exploratory high dimensional data analysis
tasks: classification, clustering, and search. For classification tasks,
as shown in the sketches example, the sage display decreases the number of 
overlapping points between classes and provides better visual separation between
classes compared to the regular tour.  For clustering tasks, as shown in the 
single cell RNA-seq example, the sage display uncovered clusters that were 
originally obscured by data piling. Furthermore, unlike some
non-linear dimension reduction (NLDR) techniques like t-SNE, the sage display 
still gives the viewer an accurate assessment of the size of a cluster, 
and their relative orientation; we learned that yellow and blue clusters have
less separation in high dimensional space than the clustering algorithm suggests.
For search tasks, as shown in the pollen and pdfsense examples, the sage display
allows to find hidden signal that is concealed by the density of points around
the center of the projection. In the pdfsense example, by zooming in on the 
points in the blue cluster we saw how they were present in all directions of the
parameter space, which was difficult to see with the regular tour.

For the sage display tuning is often required to avoid bunching points in the 
visualisation, especially if the projection is dense in the center of the 
distribution. Expanding around the center aggressively can introduce distortions
in the display, a well known problem for other NLDR methods as well.
However, unlike those methods, the parameters in the sage display are 
interpretable; we know the effect of altering $\gamma$ and $R$ on the resulting 
visualisation. Our parameter tuning example highlights this: the sage display is 
linear up to a  given effective dimension; the default sage display, preserves 
the correlation between the variables which is broken once points get moved
to the edge of the hypersphere as $\gamma$ and $R$ are changed. Given
that the display is quick to compute, being able to modify these parameters in 
real time with an interactive interface would be beneficial.  Currently, the 
sage display is naive to information in high dimensional space that is not 
captured by linear projections. Like t-SNE, it would be interesting to explore
transformations of projections where points in the high dimensional space are 
locally dense instead of expanding from the center of the distribution.
